---
title: "LoggingLab"
subtitle: "Logging simulator"
output: rmarkdown::html_vignette
df_print: kable
vignette: >
  %\VignetteIndexEntry{LoggingLab}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", echo = T, message = T, warning = F, cache = F
)
```

# The different stages of Reduced Impact Logging (RIL) described by the ONF (Office National des Forêts) of French Guiana
1) Definition of the area to be logged
2) The layout of the main skidding trails
3) Tree selection
4) Selection of trees by the logger
5) The layout of secondary skidding trails
6) Felling of the tree
7) Adjustment of secondary skidding trails in the case of Fuel Wood Exploitation (FWE)
8) Moving the bole

# Load LoggingLab and datasets
**Install LoggingLab**
```{r, eval=F}
install.packages("LoggingLab")
# devtools::install_github("VincyaneBadouard/LoggingLab", build_vignettes = TRUE) # Development version
```
**Load the package**
```{r setup}
library(LoggingLab)
library(knitr)
library(kableExtra)
library(ggplot2)
library(raster)
library(dplyr)
```
**Load the data stored in the package**
```{r}
# 2016 inventory of Paracou (French Guiana) plot 6
data(Paracou6_2016)
# Table of species exploitability criteria
data(SpeciesCriteria)
# Volume parameters table
data(ForestZoneVolumeParametersTable)
# Crown diameter allometry parameters table
data(ParamCrownDiameterAllometry)
# Digital terrain model (DTM) of the inventoried plot (1m resolution)
data(DTMParacou)
# Mask of the inventoried plot (1m resolution)
data(PlotMask)
# Relative (vertical and horizontal) distances from nearest channel network, of the inventoried plot
data(CreekDistances)
```

# Required format of the inventory
\code{\link{Paracou6_2016}}

The columns required for the package are:
  - *Forest* (to apply the corresponding volume formula)
  - *Plot* (1 value)
  - *CensusYear* (1 value)
  - *PlotArea*
  - *idTree*
  - *Xutm* and *Yutm*
  - *CodeAlive*
  - *Family*, *Genus*, *Species* and *VernName*
  - *Circ* or *CircCorr*
```{r}
# inventory class
class(Paracou6_2016)
#The name and class of all the data variables
lapply(Paracou6_2016, class)

Paracou6_2016 %>%
  dplyr::slice(1:10) %>% 
  kable() %>%
  kable_styling(font_size = 10, latex_options = "scale_down")
```
# Required format of the species exploitability criteria
\code{\link{SpeciesCriteria}}
```{r}
# speciescriteria class
class(SpeciesCriteria)
#The name and class of all the data variables
lapply(SpeciesCriteria, class)
kable(SpeciesCriteria)
```
# Required format of the volume parameters
\code{\link{ForestZoneVolumeParametersTable}}
```{r}
# volumeparameters class
class(ForestZoneVolumeParametersTable)
#The name and class of all the data variables
lapply(ForestZoneVolumeParametersTable, class)
kable(ForestZoneVolumeParametersTable)
```
# Required format of the crown diameter allometry parameters
\code{\link{ParamCrownDiameterAllometry}}
```{r}
# crowndiameterparameters class
class(ParamCrownDiameterAllometry)
#The name and class of all the data variables
lapply(ParamCrownDiameterAllometry, class)
kable(dplyr::slice_sample(ParamCrownDiameterAllometry, n=15))
```

# All the functions of the package
loggingsimulation
loggingparameters
scenariosparameters
inventorycheckformat
addtreedim
treeselection
commercialcriteriajoin
harvestable
selected
futurereserve
treefelling
createcanopy
treefromthesky
directionalfellingsuccessdef
felling1tree
rotatepolygon
getgeometry
timberharvestedvolume
exploitablefuelwoodvolume


# Arguments presentation

+ **inventory** : Input forest inventory for 1 plot and 1 census year (see the inputs formats and metadata in the
vignette or in \code{\link{Paracou6_2016}}) (data.frame)

The columns required for the package are:
  - *Forest* (to apply the corresponding volume formula)  
  - *Plot* (1 value)  
  - *CensusYear* (1 value)  
  - *PlotArea*  
  - *idTree*  
  - *Xutm* and *Yutm*  
  - *CodeAlive*  
  - *Family*, *Genus*, *Species* and *VernName*  
  - *Circ* or *CircCorr*  


+ **plotmask** Inventoried plot mask (SpatialPolygonsDataFrame **with a crs in UTM**)

+ **topography** : Digital terrain model (DTM) of the inventoried plot (LiDAR, 1m resolution)
(RasterLayer **with a crs in UTM**) (See \code{\link{DTMParacou}})
We advise you to generate your raster with Qgis rather than with the 'raster' package on R.


+ **creekdistances** Relative (vertical (*distvert*) and horizontal (*disthorz*)) distances
from nearest channel network (list of 2 large RasterLayers **with a crs in UTM**)
To generate creek distances: \code{\link{CreekDistances}} in 'Articles'.

+ **speciescriteria** : Table of species exploitability criteria : species
names, economic interest level, minimum and maximum felling diameter, in
the same format of \code{\link{SpeciesCriteria}} (2 levels of commercial
species) (data.frame)

+ **volumeparameters** : Volume parameters table (in the same format of
\code{\link{ForestZoneVolumeParametersTable}}) to compute the harvestable
volume of each tree, depend to its geographic zone if several locations
(data.frame)("Guide de Sylviculture", ONF ('Office National des Forêts') of French Guiana, 2014)

+ **scenario** : Logging scenario: "**RIL1**", "**RIL2broken**", "**RIL2**", "**RIL3**",
"**RIL3fuel**", "**RIL3fuelhollow**" or "**manual**"(character) (See *ScenariosTable*)

+ **objective** : Objective volume (m3/ha) (numeric)

+ **fuel** : Fuel wood exploitation: **no exploitation** = "**0**",
**damages and unused part of logged trees** exploitation in fuel = "**1**",
exploitation of **hollow trees, damages and unused part of logged trees** in
fuel = "**2**"

+ **diversification** : Possibility to log other species in addition to the
main commercial species (species with a value of 2 for commercial in the
\code{\link{SpeciesCriteria}} table) (logical)

+ **winching** :  Tree recovery:
"**0**": No cable or grapple  
"**1**": only **cable**  
"**2**": **grapple + cable** (grapple priority)  

+ **directionalfelling** : Directional felling =  
"0": only to direct the foot of the tree towards the trail  
"1": to direct the foot of the tree towards the trail + to avoid damage to future and reserve trees  
"2": to avoid damage to future and reserve trees + orientation angle to the trail  


+ **specieslax** : Allow diversification if stand is too poor to reach the
objective volume without diversification, = FALSE by
default (logical)

+ **objectivelax** : Allow exploitation in case of non-achievement of the
objective volume (if stand too poor), = FALSE by default (logical)

+ **crowndiameterparameters** : Crown diameter allometry parameters table (in
the same format of \code{\link{ParamCrownDiameterAllometry}}) to compute
the crown diameter of each tree, depend to its DBH (Diameter at Breast
Height) and its Species, Genus or Family names (Aubry-Kientz et al.2019). (data.frame)

+ **advancedloggingparameters** : Other parameters of the logging simulator
\code{\link{loggingparameters}} (list)

+ **iter** : Number of iterations (numeric). Default = 1.
+ **cores** : Number of cores for parallelization (numeric). Default = 1.

# The scenarios
\code{\link{ScenariosTable}}
```{r}
data(ScenariosTable)
kable(ScenariosTable)
```


# Advanced logging parameters
\code{\link{loggingparameters}}

**Default values**

*Numeric values*

+ **Minimum DBH for inclusion in the forest inventory** = 10 cm 
+ **Maximum trail centerline slope** = 22 % 
+ **Maximum trail cross slope** = 4 % 
+ **Maximum slope accessible by the grapple** = 20 % 
+ **Maximum slope around the tree to access it with cable** = 35 % 
+ **Plateau maximum slope** = 5 % 
+ **Distance to compute slope** = 3 m (for each side)  
+ **Water sources buffer zone** = 30 m
+ **Buffer zone** based on **relative elevation to the nearest water source** = 2 m
+ **Minimum main trail width** = 5 m 
+ **Maximum main trail width** = 6 m 
+ **Secondary trail width** = 4 m 
+ **Minimum DBH of trees to be avoided by trails** = 50 cm
+ **Distance of DTM resampling to erase microtopographic variation**  = 5 m
+ **Secondary trails smoothing factor** = 5 (unitless)
+ **Cable length** = 40 m 
+ **Grapple length** = 6 m 
+ **Minimum distance to consider a tree "isolated"** from other trees of its species, in the aggregative species case
(\code{\link{SpeciesCriteria}}, 'Aggregative' column) = 100 m 
+ **Future trees minimum diameter** = 35 cm (future trees are only commercial species of the 1st economic level)
+ **Proportion of successful directional felling events** = 60 %
+ **Minimum orientation of the tree fall to the trail** = 30 degree 
+ **Maximum orientation of the tree fall to the trail** = 45 degree 
+ **Part taken from hollow trees for fuel exploitation** = 1/3 
+ **Purge (unused part of the log)** = 0.14 m^3 of fuel wood/m^3 of logged trees
+ **Maximum trail density** = 200 m/ha (has no impact on the simulation.
A message will be sent to inform if this threshold has been exceeded)
+ **Maximum landing area** = 1500 m2 (has no impact on the simulation.
A message will be sent to inform if this threshold has been exceeded)

+ **Cost matrix for optimized trail layout**:
Gives an increasing cost according to a slope gradient, and
different costs on certain cases:
  - "Initial" (default = 1000)
  - "Access" (default = Inf)
  - "BigTrees" (default = 500)
  - "Reserves" (default = 500)
  - "Futures" (default = 50)
  - "MainTrails" (default = 1E-4)
  - "SecondTrails" (default = 0.1)

*Models*   

+ **Tree harvestable volume** allometry (French Guiana ONF formula):
aCoef + bCoef * (DBH/100)^2,
aCoef and bCoef depend on the forest location, stored in \code{\link{ForestZoneVolumeParametersTable}}, DBH in cm.

+ **Trunk height** allometry (from the cylinder volume formula):
CylinderVolume = pi(((DBH/100)/2)^2 x H,
DBH in cm, height (H) in m. 

+ **Tree height** allometry parameters estimated from Guyanese data with the BIOMASS package:
log(H) = 0.07359191 + 1.34241216 log(DBH) + (-0.12282344)*log(DBH)^2,
height (H) in m, DBH in cm

+ **Crown diameter allometry** (Aubry-Kientz et al.2019): ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺,
with 𝜺~N(0,σ^2) and mean σ^2 = 0.0295966977
with the crown diameter (CD) and the tree height (H) in m, and the DBH (D) in cm.

+ **Rotten model**, estimates the tree probability of being probed hollow:
1 / (1 + exp(-(-5.151 + 0.042 DBH))), with DBH in cm (developed by S.Schmitt)

+ **Visibly defect model**, estimates the commercial tree probability
to have visible defects: 1 / (1 + exp(-(-3.392 + 0.357 * Log(DBH))))
with DBH in cm (developed by V.Badouard)


# Harvest in 1 function

**Description**: Simulates a timber and fuel wood exploitation on a forest plot, in the way of Reduced Impact Logging (RIL). It covers: harvestable zones definition, tree selection, secondary skidding trails layout, tree felling, timber harvested, fuel wood volume and short-term damages quantification. This simulator is individual-centred, spatialised, and takes into account the topography and the hydrographic network.

```{r}
Rslt <- loggingsimulation1(Paracou6_2016,
                           plotmask = PlotMask, topography = DTMParacou,
                           creekdistances  = CreekDistances, speciescriteria = SpeciesCriteria,
                           volumeparameters = ForestZoneVolumeParametersTable,
                           scenario = "manual", objective = 20,
                           fuel = "2", winching = "2", directionalfelling = "2", 
                           diversification = TRUE, specieslax = FALSE, objectivelax = TRUE,
                           crowndiameterparameters = ParamCrownDiameterAllometry,
                           advancedloggingparameters = loggingparameters())

```
With the ability to iterate and parallelize:
```{r}
Rslt_iter <- loggingsimulation(Paracou6_2016,
                               plotmask = PlotMask, topography = DTMParacou,
                               creekdistances  = CreekDistances, speciescriteria = SpeciesCriteria,
                               volumeparameters = ForestZoneVolumeParametersTable,
                               scenario = "manual", objective = 20,
                               fuel = "2", winching = "2", directionalfelling = "2", 
                               diversification = TRUE, specieslax = FALSE, objectivelax = TRUE,
                               crowndiameterparameters = ParamCrownDiameterAllometry,
                               advancedloggingparameters = loggingparameters(),
                               iter = 2, cores = 2)
```
The harvestable volume may change from one simulation to another because the identification of defect trees contains a random component.
, eval = F
```{r, eval = F}
SimulTime <- microbenchmark::microbenchmark(
  
  loggingsimulation1(
    inventory = Paracou6_2016,
    plotmask = PlotMask, topography = DTMParacou,
    creekdistances  = CreekDistances, speciescriteria = SpeciesCriteria,
    volumeparameters = ForestZoneVolumeParametersTable,
    scenario = "RIL3",
    objectivelax = TRUE,
    crowndiameterparameters = ParamCrownDiameterAllometry), # 2005.819 s
  
  loggingsimulation(
    inventory = Paracou6_2016,
    plotmask = PlotMask, topography = DTMParacou,
    creekdistances = CreekDistances, speciescriteria = SpeciesCriteria,
    volumeparameters = ForestZoneVolumeParametersTable,
    scenario = "RIL3", objectivelax = TRUE,
    crowndiameterparameters = ParamCrownDiameterAllometry, # 1632.843	s
    iter = 2, cores = 2), times = 1L
)
```

```{r}
# RIL1_Rslt <- loggingsimulation(Paracou6_2016,
#                                topography = DTMParacou, verticalcreekheight  = DTMParacou,
#                                speciescriteria = SpeciesCriteria,
#                                volumeparameters = ForestZoneVolumeParametersTable,
#                                scenario = "RIL1", specieslax = FALSE, objectivelax = TRUE,
#                                crowndiameterparameters = ParamCrownDiameterAllometry,
#                                advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary1(RIL1_Rslt)
# # Without diversification the harvestable volume is too poor
```

```{r}
# RIL2broken_Rslt <- loggingsimulation(Paracou6_2016,
#                                      topography = DTMParacou, verticalcreekheight  = DTMParacou,
#                                      speciescriteria = SpeciesCriteria,
#                                      volumeparameters = ForestZoneVolumeParametersTable,
#                                      scenario = "RIL2broken", specieslax = FALSE, objectivelax = TRUE,
#                                      crowndiameterparameters = ParamCrownDiameterAllometry,
#                                      advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary1(RIL2broken_Rslt)
# RIL2broken_inventory <- RIL2broken_Rslt$inventory
# # Without diversification the harvestable volume is too poor
# # Not all harvestable trees are always harvested because they are eventually probed hollow, and there is not always a harvestable tree to replace them.
```

```{r}
# RIL2_Rslt <- loggingsimulation(Paracou6_2016,
#                                topography = DTMParacou, verticalcreekheight  = DTMParacou,
#                                speciescriteria = SpeciesCriteria,
#                                volumeparameters = ForestZoneVolumeParametersTable,
#                                scenario = "RIL2", specieslax = FALSE, objectivelax = TRUE,
#                                crowndiameterparameters = ParamCrownDiameterAllometry,
#                                advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary1(RIL2_Rslt)
# # Without diversification the harvestable volume is too poor
```

```{r}
# RIL3_Rslt <- loggingsimulation(Paracou6_2016,
#                                topography = DTMParacou, verticalcreekheight  = DTMParacou,
#                                speciescriteria = SpeciesCriteria,
#                                volumeparameters = ForestZoneVolumeParametersTable,
#                                scenario = "RIL3", specieslax = FALSE, objectivelax = TRUE,
#                                crowndiameterparameters = ParamCrownDiameterAllometry,
#                                advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# 
# RIL3_inventory <- RIL3_Rslt$inventory
# loggingsummary1(RIL3_Rslt)
# # With diversification the harvestable volume is much higher
# # but 30m3/ha is a too high objective for this plot size
# # Not all harvestable trees are always harvested because they are eventually probed hollow, and there is not always a harvestable tree to replace them.
```

```{r}
# RIL3fuel_Rslt <- loggingsimulation(Paracou6_2016,
#                                    topography = DTMParacou, verticalcreekheight  = DTMParacou,
#                                    speciescriteria = SpeciesCriteria,
#                                    volumeparameters = ForestZoneVolumeParametersTable,
#                                    scenario = "RIL3fuel", specieslax = FALSE, objectivelax = TRUE,
#                                    crowndiameterparameters = ParamCrownDiameterAllometry,
#                                    advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary1(RIL3fuel_Rslt)
# # Not all harvestable trees are always harvested because they are eventually probed hollow, and there is not always a harvestable tree to replace them.
```

```{r}
# RIL3fuelhollow_Rslt <- loggingsimulation(Paracou6_2016,
#                                          topography = DTMParacou, verticalcreekheight  = DTMParacou,
#                                          speciescriteria = SpeciesCriteria,
#                                          volumeparameters = ForestZoneVolumeParametersTable,
#                                          scenario = "RIL3fuelhollow",
#                                          specieslax = FALSE, objectivelax = TRUE,
#                                          crowndiameterparameters = ParamCrownDiameterAllometry,
#                                          advancedloggingparameters = loggingparameters(),
#                                          iter = 1, cores = 1)
# RIL3fuelhollow_inventory <- RIL3fuelhollow_Rslt$inventory
# # loggingsummary1(RIL3fuelhollow_Rslt)
```

## Results summary

**Description**: Returns a summary of the outputs of the loggingsimulation function (console display): a reminder of the inputs and the iterations statistics (mean, standard deviation, quantiles) of the outgoing figures.

```{r}
data(LoggingSimulationOutputs) # Outputs of one logging simulation
data(LoggingSimulationOutputs_iter) # Outputs of one logging simulation (2 iterations and 2 cores)
loggingsummary1(LoggingSimulationOutputs)
loggingsummary(LoggingSimulationOutputs_iter) # Outputs of one logging simulation (2 iterations and 2 cores))
```

# Decomposed harvesting

## Check & format input inventory data for the "LoggingLab" package

**Description**:
* inventorycheckformat() checks if the input inventory data is compatible with the ‘LoggingLab’ package and returns the inventory if the inventory is in the required format or stop the function if the format is not the one required.
* cleaninventory()returns the inventory with **only alive trees within the inventoried plot**.
  

```{r}
inventory <- inventorycheckformat(Paracou6_2016)
inventory <- cleaninventory(inventory, PlotMask, loggingparameters())
```

## Compute tree dimensions

**Description**: Compute tree dimensions (**tree**, **trunk** and **crown height**, **crown diameter**, **harvestable volume**, wood density, and AGB)

```{r}
inventory <- addtreedim(inventory, volumeparameters = ForestZoneVolumeParametersTable)
```

## Main skidding trails opening

**Description**: Generates the main trail of the inventoried plot, as lines at the edge and outside of the plot.

```{r}
MainTrails <- maintrailextract(DTMParacou)

# # To map a raster with ggplot : https://erinbecker.github.io/r-raster-vector-geospatial/02-raster-plot/index.html
# ## convert to a df for plotting in two steps,
# ## First, to a SpatialPointsDataFrame
# DTMParacou_pts <- rasterToPoints(DTMParacou, spatial = TRUE)
# ## Then to a 'conventional' dataframe
# DTMParacou_df  <- data.frame(DTMParacou_pts)


plot(DTMParacou)
plot(MainTrails, add = T)
```

## Harvestable area definition

**Description**: Defines harvestable zones and machine-accessible zones within the plot.

By default, a prospecting unit is an area connected to a truck trail or a main skid trail, with a slope of less than 27%, avoiding lowlands and the water system (30 m buffer).

```{r}
HarvestableAreaOutputs <- harvestableareadefinition(
  topography = DTMParacou,
  creekdistances = CreekDistances,
  maintrails = MainTrails,
  plotmask = PlotMask,
  scenario = "manual", winching = "1", # with an zone for cable only
  advancedloggingparameters = loggingparameters()
)
HarvestablePolygons <- HarvestableAreaOutputs$HarvestablePolygons
PlotSlope <- HarvestableAreaOutputs$PlotSlope
HarvestableArea <- HarvestableAreaOutputs$HarvestableArea
MachinePolygons <- HarvestableAreaOutputs$MachinePolygons

library(sf)
ggplot() +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          fill = "olivedrab", alpha = 0.1) +
  geom_sf(data = MachinePolygons,
          fill = "olivedrab", alpha = 0.5) +
  labs(alpha = "Harvestable") +
  labs(title = "Paracou P6 - Harvestable zones") +
  scale_colour_manual(values = c("Harvestable area" = "olivedrab"))
```


## Tree selection

**Description**: Selects trees to harvest, and future and reserve trees.

Trees with visible defects are identified ('VisiblyDefectModel' in 
'advancedloggingparameters' argument) and therefore not designated.

(*Objective volume*: If the user has chosen not to harvest hollow probed trees for
energy ('RottenModel' in 'advancedloggingparameters' argument), 20-30% will be
added to the objective volume in order to compensate for these designated hollow
trees. If the user has chosen to harvest the hollow probed trees as fuel wood,
he will harvest strictly his target volume, without *bonus.*)

Trees will be designated as "**harvestable**" if they:
- belonging to species of 1st economic rank or more if diversification
- DBH between the MinFD and the MaxFD.
- not isolated ( >100m ('IsolateTreeMinDistance' in \code{\link{loggingparameters}})) from other individuals of the same
species in the aggregative species case (\code{\link{SpeciesCriteria}}, 'Aggregative' column).
- on slopes < 22% ('TreeMaxSlope'in \code{\link{loggingparameters}})
- off the main trails.

If the harvestable volume is higher than the objective volume, and that diversification was not chosen, MinFD of the 1st economic rank species only is increased.
If the diversification is allowed, MinFD of 1st and 2nd economic level species is increased.
Then, the trees to be harvested are chosen in decreasing order of volume, until the objective volume is reached.

If the harvestable volume is too low, diversification can be applied if it was not already applied ('specieslax') (trees of all commercial ranks are selected in decreasing order of volume until the objective volume is reached), or harvesting can continue despite an unreached objective volume, or be abandoned ('objectivelax')

**Future** trees will be:
- species of 1st economic rank
- DBH between 35cm ('FutureTreesMinDiameter') and the species MinFD or UpMinFD if it has been raised for its species.
- in the prospection units (harvestable areas)

**Reserve** trees will be:
- future trees
- in the same number as trees to be harvested.

### In 1 function
```{r}
treeselectionoutputs <- treeselection(inventory,
                                      topography = DTMParacou,
                                      speciescriteria = SpeciesCriteria,
                                      scenario ="manual", objective = 20,
                                      fuel = "2", winching = "2",
                                      diversification = FALSE, specieslax = FALSE,
                                      objectivelax = TRUE,
                                      plotslope = PlotSlope,
                                      harvestablepolygons = HarvestablePolygons,
                                      advancedloggingparameters = loggingparameters())
```

### Decomposed tree selection
#### Joins commercial criteria table
```{r}
inventory <- commercialcriteriajoin(inventory, SpeciesCriteria)
```

#### Harvestable trees identification

**Description**: identifies harvestable trees among species of **commercial interest**, with **exploitable diameters**, then according to criteria of **slope**, **distance** to other conspecific individuals if the species is aggregative, and the **absence of visible defects**.


```{r}
harvestableOutputs <- harvestable(inventory, topography = DTMParacou,
                                  diversification = TRUE, specieslax = FALSE,
                                  plotslope = PlotSlope,
                                  harvestablepolygons = HarvestablePolygons,
                                  scenario = "manual", winching = "0",
                                  advancedloggingparameters = loggingparameters())
inventory <- harvestableOutputs$inventory
HVinit <- harvestableOutputs$HVinit
```

#### Trees to be exploited selection

**Description**: selects the trees to log among the exploitable trees, according to the objective volume and the exploitable volume on the plot.

```{r}
inventory <- selected(inventory, topography = DTMParacou,
                      scenario = "manual", fuel = "2", diversification = TRUE,
                      VO = 125, HVinit = HVinit, specieslax = FALSE, objectivelax = TRUE,
                      advancedloggingparameters = loggingparameters())$inventory
```

#### Future & reserve trees designation

**Description**: designates which trees will be harvested in future seasons: "*future trees*", and which should be protected as seed trees: "*reserve trees*".

```{r}
inventory <- futurereserve(inventory, SpeciesCriteria)
```

## Secondary skidding trails layout

**Description**: Starting from the main skidding trails, draw secondary skidding trails on the
zones accessible to the machines, allowing to collect the selected trees
with the chosen machines ("winching" argument). The layout is optimised to
reduce the distance covered while respecting topographical constraints and
avoiding trees to protect.

Skidding trail (main, secondary): allows wood to be transported from the parcel to truck routes.

The secondary skidding trails are:
- 4 m width ('ScndTrailWidth')
- 22% maximum slope in length ('MaxTrailCenterlineSlope')
- 4% maximum side slope (taken into account in the presence of LIDAR). ('MaxTrailCrossSlope')
They avoid :
- the trees to be logged
- the trees with a DBH of more than 50 cm ('BigTrees')
- the reserve trees.
They join in priority:
1: groups in decreasing order of tree abundance
2: those with the shortest distance to the nearest track
3: avoiding future trees
4: minimising slopes in length and width.

RIL1/RIL2broken: trails go to the base of trees
RIL2: cable only: trails go up to a maximum of 40 m ('CableLength') from trees.
RIL3/RIL3 including fuel: grapple (trails with longitudinal slope <20% 
('GrappleMaxslope')) (trails go up to 6 m ('GrappleLength') from the trees),
and cable (trails go up to 40 m ('CableLength') from the trees) is used only
when the longitudinal slope is greater than 20% or when the tree to be skidded
is isolated from other trees to be exploited, from 6 to 40 m.
If the crown is not accessible, it will not be harvested, only the trunk can be
used in fuel wood.

If the number of trees connected to a secondary trail exceeds 20 (''), the secondary trail will take the characteristics (width) of a main trail.

Damage :
- on the trail
- on the edge of the trail: neglected.

```{r}
ScndTrailOutputs <- secondtrailsopening(topography = DTMParacou,
                                        plotmask = PlotMask,
                                        maintrails = MainTrails,
                                        plotslope = HarvestableAreaOutputsCable$PlotSlope,
                                        harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
                                        machinepolygons = HarvestableAreaOutputsCable$MachinePolygons,
                                        treeselectionoutputs = treeselectionoutputs,
                                        scenario = "manual",
                                        winching = "2",
                                        advancedloggingparameters = loggingparameters())

inventory <- ScndTrailOutputs$inventory
SmoothedTrails <- ScndTrailOutputs$SmoothedTrails
MainTrailsAccess <- ScndTrailOutputs$MainTrailsAccess
TrailsDensity <- ScndTrailOutputs$TrailsDensity
TrailsIdentity <- ScndTrailOutputs$TrailsIdentity
RawSecondTrails <- ScndTrailOutputs$RawSecondTrails
CostRasterAgg <- ScndTrailOutputs$CostRasterAgg


# pol1 <- list(matrix(c(286503, 582925,
#                       286503, 583240,
#                       286507, 583240,
#                       286507, 582925,
#                       286503, 582925) # the return
#                     ,ncol=2, byrow=TRUE))
# pol2 <- list(matrix(c(286650, 582925,
#                       286650, 583240,
#                       286654, 583240,
#                       286654, 582925,
#                       286650, 582925) # the return
#                     ,ncol=2, byrow=TRUE))
# 
# PolList = list(pol1,pol2) #list of lists of numeric matrices
# ScndTrail <- sf::st_as_sf(sf::st_sfc(sf::st_multipolygon(PolList)))
# ScndTrail <- sf::st_set_crs(ScndTrail, sf::st_crs(MainTrails))
```
## Tree felling

**Description**: Simulates the tree felling, with the success or failure of the direction of the tree fall, foot to the trail, with an angle to the trail and avoiding the trees to protect, as desired. If FWE, the tree will be directed with its crown towards the trail (if the orientation is successful) if it can be retrieved with a grapple.

The felling of the tree creates a tree (including crown) on the ground, with dimensions calculated with specific allometries ('advancedloggingparameters').

RIL1/RIL2broken/RIL2:
- at 40%: random fall
- at 60% ('TreefallSuccessProportion'): *base of the tree towards the nearest trail* (main or 2ndary)

RIL3/RIL3 timber + fuel wood:
- at 40%: random fall
- at 60% ('TreefallSuccessProportion'):
* if RIL3 + fuel & trees < 6 m from the trail and slope <20% (*grapple* use):
- no particular angle to orientate to the trail,
only to orient the tree *crown* as close as possible to the trail
- priority 1: avoid futures and reserves,
- priority 2: conformation allowing skidding back to the main trail

* otherwise (RIL3, RIL3 + fuel &
trees > 6 m from the trail and/or slope >20%)(*cable* use):
- 30-45◦ orientation ('MinTreefallOrientation'; 'MaxTreefallOrientation')
- *base* to nearest trail
- priority 1: avoid futures and reserves
- priority 2: conformation allowing skidding back to the main trail

Damage:
Secondary windfall: *all trees under the felled tree (timber or energy) will be considered dead*.

### In 1 function
```{r}
inventory <- treefelling(inventory, scenario = "manual", fuel = "2",
                         winching = "2", directionalfelling = "2",
                         maintrailsaccess = MainTrailsAccess,
                         scndtrail = SmoothedTrails,
                         advancedloggingparameters = loggingparameters())
```

## Adjusted secondary skidding trails layout (for fuel wood harvesting only (fuel = "1" or "2"))

**Description**: In the FWE (Fuel Wood Exploitation) case, the layout of the
skidding trails is redefined to favour the recovery of trees through the crown (only
with a grapple) in order to use the crowns for fuel wood.

```{r}
ScndTrailAdjustOutputs <- secondtrailsadjusted(inventory = inventory,
                                               topography = DTMParacou,
                                               plotmask = PlotMask,
                                               maintrails = MainTrails,
                                               plotslope = PlotSlope,
                                               harvestablepolygons = HarvestablePolygons,
                                               machinepolygons = MachinePolygons,
                                               maintrailsaccess = MainTrailsAccess,
                                               scenario = "manual",
                                               winching = "2",
                                               advancedloggingparameters = loggingparameters())

inventory <- ScndTrailAdjustOutputs$inventory
AdjustSmoothedTrails <- ScndTrailAdjustOutputs$SmoothedTrails
AdjustTrailsDensity <- ScndTrailAdjustOutputs$TrailsDensity
AdjustTrailsIdentity <- ScndTrailAdjustOutputs$TrailsIdentity
AdjustRawSecondTrails <- ScndTrailAdjustOutputs$RawSecondTrails
```

## Quantify the volumes achieved

By default, within a hollow tree, 2/3 of the log will be usable as timber,
1/3 as fuel wood ('TreeHollowPartForFuel').
For dead trees from the operation (skidding trails, secondary windfall),
the whole trunk will be exploitable as fuel wood.

### Compute the timber harvested volume

**Description**: Computes the timber harvested volume in healthy trees exploited for timber, and in the hollow trees if they are also harvested for fuel wood.

```{r}
TimberV <- timberharvestedvolume(inventory, scenario = "manual", fuel = "2",
                                 advancedloggingparameters = loggingparameters())

TimberLoggedVolume <- TimberV$TimberLoggedVolume
NoHollowTimberLoggedVolume <- TimberV$NoHollowTimberLoggedVolume
```

### Compute the exploitable fuel wood volume

**Description**: Computes the exploitable fuel wood volume in healthy trees exploited for timber (their unused part), in the hollow trees and in the damage trees (caused by skidding trails, secondary windfall).

```{r}
FuelV <- exploitablefuelwoodvolume(inventory, scenario = "manual", fuel = "2",
                                   TimberLoggedVolume = TimberLoggedVolume,
                                   NoHollowTimberLoggedVolume = NoHollowTimberLoggedVolume,
                                   advancedloggingparameters = loggingparameters())

DamageVolume <- FuelV$DamageVolume # only damage (without purge and hollow trees)
FuelVolume <- FuelV$FuelVolume
```

# Outputs
Format: A large list of 38 elements  

+ **inventory** : Output forest inventory (data.frame)  

Numeric values:  
+ **HarvestableArea** : Harvestable area in ha (numeric)  
+ **VO** : Objective volume in m3 (numeric)  
+ **HVinit** : Initial harvestable volume in m3 (numeric)  
+ **TimberLoggedVolume** : Timber logged volume in m3 (numeric)  
+ **NoHollowTimberLoggedVolume** : No hollow timber logged volume (only healthy trees) in m3 (numeric)  
+ **FuelVolume** : Fuel wood volume in m3 (numeric)  
+ **DamageVolume** : Damages volume (only damages (= without purge and hollow trees)) in m3 (numeric)  
+ **LostBiomass** : Total lost biomass in ton (numeric)  
+ **TrailsDensity** : Skidding trails density (preliminary if FWE) in m/ha (units)  
+ **AdjustTrailsDensity** : Adjusted skidding trails density if FWE in m/ha (units)  

Spatial objects:  
+ **MainTrails** : Main skidding trails (sf)  

+ **HarvestablePolygons** : Harvestable zones (MULTIPOLYGON with crs)  
+ **MachinePolygons** : Exploitable zones accessible to machines (MULTIPOLYGON with crs)  
+ **PlotSlope** : Slopes of the plot (in radians) (RasterLayer with crs)  

+ **SmoothedTrails** : Smoothed secondary skidding trails (MULTIPOLYGON with crs)  
+ **MainTrailsAccess** : Random access point of main trail for each harvestable zone (POINT with crs)  
+ **TrailsIdentity** : Information on sections of the trails (matrix), with
   - LineID: 
   - LoggedTrees: idTree of trees reached by the trails
   - TypeExpl: type of winching  
+ **RawSecondTrails** : Non-smoothed secondary skidding trails (SpatialLines with crs)  
+ **CostRasterAgg** : The cost raster (RasterLayer)  

+ **AdjustSmoothedTrails** : Adjusted smoothed secondary skidding trails for FWE (MULTIPOLYGON with crs)  
+ **AdjustTrailsIdentity** : Adjusted version of TrailsIdentity for FWE (matrix)  
+ **AdjustRawSecondTrails** : Adjusted non-smoothed secondary skidding trails for FWE (SpatialLines with crs)  

POINTS:  
+ **HarvestableTreesPoints** : Harvestable trees points (sf)  
+ **SelectedTreesPoints** : Selected trees points (sf)  
+ **FutureTreesPoints** : Future trees points (sf)  
+ **ReserveTreesPoints** : Reserve trees points (sf)  
+ **HollowTreesPoints** : Hollow trees points (sf)  
+ **EnergywoodTreesPoints** : Energywood trees points (sf) 

INPUTS reminder:  
+ **INPUTinventory** : Input forest inventory (data.frame)  
+ **scenario** : Input value for 'scenario' argument(character)  
+ **objective** : Input value for 'objective' argument (numeric)  
+ **fuel** : Input value for 'fuel' argument (character)  
+ **diversification** : Input value for 'diversification' argument (logical)  
+ **winching** : Input value for 'winching' argument (numeric)  
+ **directionalfelling** : Input value for 'directionalfelling' argument (character)  
+ **specieslax** : Input value for 'specieslax' argument (logical)  
+ **objectivelax** : Input value for 'objectivelax' argument (logical)  

# Tool functions

'inventorycheckformat' check if the input inventory data is compatible with the "LoggingLab" package (see 'Required format of the inventory' section of the vignette)

'addtreedim' compute tree dimensions with the 'advancedloggingparameters' argument:
- Tree height (in m) ('TreeHeightAllometry')
- Tree Harvestable Volume (m^3) ('TreeHarvestableVolumeAllometry')
- Trunk height (in m) ('TrunkHeightAllometry')
- Crown height (in m)
- Crown diameter (in m) ('CrownDiameterAllometry')
- Wood density (g/cm^3) (by BIOMASS package)
- Tree above-ground biomass (AGB) (in Mg) (by BIOMASS package)

```{r include=FALSE}
inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
                        volumeparameters = ForestZoneVolumeParametersTable)
```


## Get geometry
Converts a dataframe with a column of characters, which contains the WKT encoded geometries, into an sf object. The column is converted to sfc.

## Create the canopy

'createcanopy' function return a dataframe with a column 'Crowns' containing the ellipses
(*sfc_POLYGON*) as trees crown, with their diameter filled in,
representing trees from the sky.
```{r}
canopy <- createcanopy(inventory)

# The small ones first so that they are behind the big ones on the plot
canopy <- dplyr::arrange(canopy, TreeHeight)
ggplot() +
  geom_sf(data = getgeometry(canopy, Crowns),
          aes(alpha = TreeHeight),
          fill = "forestgreen") +
  labs(alpha = "Tree height")
```

## 1 tree from the sky

'createcanopy' function return an ellipse (*sfc_POLYGON*) as a crown, with its diameter filled in, representing the tree from the sky.
```{r}
dat <- inventory %>% 
  filter(CrownDiameter == max(CrownDiameter))

Crown <- treefromthesky(dat)

ggplot() +
  geom_sf(data = sf::st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
  geom_sf(data = Crown, fill = "forestgreen") # trees polygons
```

directionalfellingsuccessdef
felling1tree


## Rotate a polygon 
Rotate the input polygon with a given angle and around a fix point.

With:
*p* a polygon (POLYGON or sfc_POLYGON)
*angle* the angle in degrees in the clockwise direction (numeric)
*fixed* a fix point around which the polygon will be rotated (POINT)

Function adapted from Jeffrey Evans' 'rotate.polygon' function:
https://github.com/jeffreyevans/spatialEco/blob/master/R/rotate.polygon.R

```{r}
NotAPol <- matrix(c(286503, 583134,
                    286503, 583240,
                    286507, 583240,
                    286507, 583134,
                    286503, 583134)
                  ,ncol=2, byrow=TRUE)
Pol <- sf::st_polygon(list(NotAPol))

Point <- sf::st_point(c(286505,583134))

Rslt <- rotatepolygon(p = Pol, angle = 10, fixed = Point)
plot(Rslt)
```






