---
title: "Maria"
subtitle: "Logging simulator"
output: rmarkdown::html_vignette
df_print: kable
vignette: >
  %\VignetteIndexEntry{Maria}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", echo = T, message = T, warning = F, cache = T
)
```

# Load Maria and datasets
**Install Maria**
```{r, eval=F}
install.packages("Maria")
```
**Load the package**
```{r setup}
library(Maria)
library(knitr)
library(kableExtra)
library(ggplot2)
```
**Load the two datasets stored in the package**
```{r}
# 2016 inventory of Paracou (French Guiana) plot 6
data(Paracou6_2016)
# Table of species exploitability criteria
data(SpeciesCriteria)
# Volume parameters table
data(ForestZoneVolumeParametersTable)
# Crown diameter allometry parameters table
data(ParamCrownDiameterAllometry)
# Digital terrain model (DTM) of the plot 6 of Paracou (1m resolution, LiDAR campaign of 2016)
data(DTMParacou)
# Slopes (in radians) of the plot 6 of Paracou (with a neighbourhood of 8 cells)
data(PlotSlope)
```

# Required format of the inventory
\code{\link{Paracou6_2016}}
```{r}
# inventory class
class(Paracou6_2016)
#The name and class of all the data variables
lapply(Paracou6_2016, class)

Paracou6_2016 %>%
  dplyr::slice(1:10) %>% 
  kable() %>%
  kable_styling(font_size = 10, latex_options = "scale_down")
```
# Required format of the species exploitability criteria
\code{\link{SpeciesCriteria}}
```{r}
# speciescriteria class
class(SpeciesCriteria)
#The name and class of all the data variables
lapply(SpeciesCriteria, class)
kable(SpeciesCriteria)
```
# Required format of the volume parameters
\code{\link{ForestZoneVolumeParametersTable}}
```{r}
# volumeparameters class
class(ForestZoneVolumeParametersTable)
#The name and class of all the data variables
lapply(ForestZoneVolumeParametersTable, class)
kable(ForestZoneVolumeParametersTable)
```
# Required format of the crown diameter allometry parameters
\code{\link{ParamCrownDiameterAllometry}}
```{r}
# crowndiameterparameters class
class(ParamCrownDiameterAllometry)
#The name and class of all the data variables
lapply(ParamCrownDiameterAllometry, class)
kable(dplyr::slice_sample(ParamCrownDiameterAllometry, n=15))
```

# All the functions of the package
loggingsimulation
loggingparameters
scenariosparameters
inventorycheckformat
addtreedim
treeselection
ONFGuyafortaxojoin
harvestable
selected
futurereserve
treefelling
createcanopy
treefromthesky
directionalfellingsuccessdef
felling1tree
rotatepolygon
getgeometry
timberharvestedvolume
exploitablefuelwoodvolume


# Arguments presentation

+ **inventory** : Your inventory (see the inputs formats and metadata in the
\code{\link{vignette}}) (data.frame)

+ **topography** : Digital terrain model (DTM) of the inventoried plot (LiDAR
or SRTM) (RasterLayer)

+ **relativeelevation** : (RasterLayer)

+ **speciescriteria** : Table of species exploitability criteria : species
names, economic interest level, minimum and maximum felling diameter, in
the same format of \code{\link{SpeciesCriteria}} (2 levels of commercial
species) (data.frame)

+ **volumeparameters** : Volume parameters table (in the same format of
\code{\link{ForestZoneVolumeParametersTable}}) to compute the harvestable
volume of each tree, depend to its geographic zone if several locations
(data.frame)

+ **scenario** : Logging scenario: "**RIL1**", "**RIL2broken**", "**RIL2**", "**RIL3**",
"**RIL3fuel**", "**RIL3fuelhollow**" or "**manual**"(character)

+ **objective** : Objective volume per hectare (numeric)

+ **fuel** : Fuel wood exploitation: **no exploitation** = "**0**", **damages and purge**
exploitation in fuelwood = "**1**", exploitation of **hollow trees, damages and purge** in
fuelwood = "**2**"

+ **diversification** : Taking of other species in addition to the main
commercial species (2 levels of commercial species in the
\code{\link{SpeciesCriteria}} table) (logical)

+ **winching** : No cable or grapple = "**0**", only **cable** = "**1**", **grapple + cable**
= "**2**"

+ **directionalfelling** : Directional felling = "**0**" (absent), "**1**" (only to
avoid damage to future and reserve trees), "**2**" (avoid damage to future and
reserve trees + track orientation)

+ **specieslax** : Allow diversification if stand is too poor, = FALSE by
default (logical)

+ **objectivelax** : Allow exploitation in case of non-achievement of the
objective volume (if stand too poor), = FALSE by default (logical)

+ **crowndiameterparameters** : Crown diameter allometry parameters table (in
the same format of \code{\link{ParamCrownDiameterAllometry}}) to compute
the crown diameter of each tree, depend to its DBH (Diameter at Breast
Height) and its species, genus or family. (data.frame)

+ **advancedloggingparameters** : Other parameters of the logging simulator
\code{\link{loggingparameters}} (list)

+ **iter** : Number of iterations (numeric). Default = 1.
+ **cores** : Number of cores for parallelization (numeric). Default = 1.

# The scenarios
\code{\link{ScenariosTable}}
```{r}
data(ScenariosTable)
kable(ScenariosTable)
```


# Advanced logging parameters
\code{\link{loggingparameters}}

**Default values**

*Numeric values*

+ **Minimum DBH value** = 10 cm 
+ **Maximum area slope** = 27 % 
+ **Maximum main & 2nd trail centerline slope** = 22 % 
+ **Maximum main & 2nd trail cross slope** = 4 % 
+ **Grapple maximum slope** = 20 % 
+ **Maximum tree slope** = 22 % 
+ **Plateau maximum slope** = 5 % 
+ **Distance to compute slope** = 6 m (3m for each side) 
+ **Water sources buffer zone** = 30 m
+ **Minimum main trail width** = 5 m 
+ **Maximum main trail width** = 6 m 
+ **2nd trail width** = 4 m 
+ **DBH of trees to be avoided at trail construction** = 50 cm 
+ **Objective bonus** = 30 % (20;30%) 
+ **Cable length** = 40 m 
+ **Grapple length** = 6 m 
+ **Minimum distance to consider a tree "isolated"** from other trees of its species = 100 m 
+ **Future trees minimum diameter** = 35 cm 
+ **Proportion of successful felling cases** = 0.6 %
+ **Minimum orientation of the tree fall to the trail** = 30 degree 
+ **Maximum orientation of the tree fall to the trail** = 45 degree 
+ **Part taken from hollow trees for fuel exploitation** = 1/3 
+ **Purge** = 0.14 m^3 of fuelwood/m^3 of logged trees
+ **Maximum trail density** = 200 m/ha (has no impact on the simulation.
A message will only be sent to inform you of its validation or not)
+ **Maximum landing area** = 1500 square meters (has no impact on the simulation.
A message will only be sent to inform you of its validation or not)

*Models*   

+ **Tree harvestable volume** allometry (French Guiana ONF formula):
aCoef + bCoef * (DBH/100)^2,
aCoef and bCoef depend on the forest location, DBH in cm.

+ **Trunk height** allometry (from the cylinder volume formula):
CylinderVolume = pi(((DBH/100)/2)^2 x H,
DBH in cm, height (H) in m. 

+ **Tree height** allometry (from the *BIOMASS* package):
log(H) = 0.07359191 + 1.34241216 log(DBH) + -0.12282344 log(DBH)^2,
height (H) in m, DBH in cm

+ **Crown diameter allometry** (*ref*): ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺,
with 𝜺~N(0,σ^2) and mean σ^2 = 0.0295966977
with the crown diameter (CD) and the tree height (H) in m, and the DBH (D) in cm.

+ **Rotten model**, estimates the tree probability of being probed hollow:
1 / (1 + exp(-(-5.151 + 0.042 DBH))), with DBH in cm 

+ **Visibly defect model**, estimates the tree probability
to have visible defects: 1 / (1 + exp(-(-3.392 + 0.357 * Log(DBH))))
with DBH in cm


# Harvest in 1 function
```{r}
Rslt <- loggingsimulation(Paracou6_2016,
                          topography = DTMParacou, relativeelevation  = DTMParacou,
                          speciescriteria = SpeciesCriteria,
                          volumeparameters = ForestZoneVolumeParametersTable,
                          scenario = "manual", objective = 20,
                          fuel = "2", diversification = TRUE, winching = "2",
                          directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE,
                          crowndiameterparameters = ParamCrownDiameterAllometry,
                          advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
```

```{r}
# RIL1_Rslt <- loggingsimulation(Paracou6_2016,
#                           topography = DTMParacou, relativeelevation  = DTMParacou,
#                           speciescriteria = SpeciesCriteria,
#                           volumeparameters = ForestZoneVolumeParametersTable,
#                           scenario = "RIL1", specieslax = FALSE, objectivelax = TRUE,
#                           crowndiameterparameters = ParamCrownDiameterAllometry,
#                           advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary(RIL1_Rslt)
```

```{r}
# RIL2broken_Rslt <- loggingsimulation(Paracou6_2016,
#                           topography = DTMParacou, relativeelevation  = DTMParacou,
#                           speciescriteria = SpeciesCriteria,
#                           volumeparameters = ForestZoneVolumeParametersTable,
#                           scenario = "RIL2broken", specieslax = FALSE, objectivelax = TRUE,
#                           crowndiameterparameters = ParamCrownDiameterAllometry,
#                           advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary(RIL2broken_Rslt)
```

```{r}
# RIL2_Rslt <- loggingsimulation(Paracou6_2016,
#                           topography = DTMParacou, relativeelevation  = DTMParacou,
#                           speciescriteria = SpeciesCriteria,
#                           volumeparameters = ForestZoneVolumeParametersTable,
#                           scenario = "RIL2", specieslax = FALSE, objectivelax = TRUE,
#                           crowndiameterparameters = ParamCrownDiameterAllometry,
#                           advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary(RIL2_Rslt)
```

```{r}
# RIL3_Rslt <- loggingsimulation(Paracou6_2016,
#                           topography = DTMParacou, relativeelevation  = DTMParacou,
#                           speciescriteria = SpeciesCriteria,
#                           volumeparameters = ForestZoneVolumeParametersTable,
#                           scenario = "RIL3", specieslax = FALSE, objectivelax = TRUE,
#                           crowndiameterparameters = ParamCrownDiameterAllometry,
#                           advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# 
# new <- RIL3_Rslt$inventory
# loggingsummary(RIL3_Rslt)
# not all of the harvestable volume is taken as there are hollow probed trees
```

```{r}
# RIL3fuel_Rslt <- loggingsimulation(Paracou6_2016,
#                           topography = DTMParacou, relativeelevation  = DTMParacou,
#                           speciescriteria = SpeciesCriteria,
#                           volumeparameters = ForestZoneVolumeParametersTable,
#                           scenario = "RIL3fuel", specieslax = FALSE, objectivelax = TRUE,
#                           crowndiameterparameters = ParamCrownDiameterAllometry,
#                           advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary(RIL3fuel_Rslt)
#Doest work, find why
```

```{r}
# RIL3fuelhollow_Rslt <- loggingsimulation(Paracou6_2016,
#                           topography = DTMParacou, relativeelevation  = DTMParacou,
#                           speciescriteria = SpeciesCriteria,
#                           volumeparameters = ForestZoneVolumeParametersTable,
#                           scenario = "RIL3fuelhollow", specieslax = FALSE, objectivelax = TRUE,
#                           crowndiameterparameters = ParamCrownDiameterAllometry,
#                           advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary(RIL3fuelhollow_Rslt)
# not all of the harvestable volume is taken as there are hollow probed trees 
```
## Results summary
```{r}
loggingsummary(Rslt)
```

# Decomposed harvesting

## Check & format your inventory data for the "Maria" package
```{r}
inventory <- inventorycheckformat(Paracou6_2016)
```

## Compute tree dimensions
**Tree and crown height and diameter, harvestable volume, wood density, and AGB**
```{r}
inventory <- addtreedim(inventory, volumeparameters = ForestZoneVolumeParametersTable)
```

## Harvestable area definition

## Tree selection
### In 1 function
**Trees to be exploited, future and reserve trees**
```{r}
# treeselectionoutputs <- treeselection(inventory,
#                                       topography = DTMParacou, plotslope = PlotSlope,
#                                       speciescriteria = SpeciesCriteria,
#                                       objective = 20, scenario ="manual", fuel = "2",
#                                       diversification = FALSE, specieslax = FALSE,
#                                       objectivelax = TRUE,
#                                       advancedloggingparameters = loggingparameters())
```

### Decomposed tree selection
#### Joins commercial criteria table
```{r}
inventory <- ONFGuyafortaxojoin(inventory, SpeciesCriteria)
```

#### Harvestable trees identification
```{r}
harvestableOutputs <- harvestable(inventory, topography = DTMParacou,
                                  diversification = TRUE, plotslope = PlotSlope, specieslax = FALSE,
                                  advancedloggingparameters = loggingparameters())
inventory <- harvestableOutputs$inventory
HVinit <- harvestableOutputs$HVinit
```

#### Trees to be exploited selection
```{r}
inventory <- selected(inventory, scenario = "manual", fuel = "2",
                      diversification = TRUE, VO = 125, HVinit = HVinit, specieslax = FALSE,
                      objectivelax = TRUE, topography = DTMParacou,
                      advancedloggingparameters = loggingparameters())$inventory
```

#### Future & reserve trees designation
```{r}
inventory <- futurereserve(inventory, SpeciesCriteria)
```

## Secondary trails layout
```{r}
MainTrail <- sf::st_linestring(matrix(c(286400, 583130,
                                        286400, 583250,
                                        286655, 583250,
                                        286655, 583130,
                                        286400, 583130) # the return
                                      ,ncol=2, byrow=TRUE))

pol1 <- list(matrix(c(286503, 583134,
                      286503, 583240,
                      286507, 583240,
                      286507, 583134,
                      286503, 583134) # the return
                    ,ncol=2, byrow=TRUE))
pol2 <- list(matrix(c(286650, 583134,
                      286650, 583240,
                      286654, 583240,
                      286654, 583134,
                      286650, 583134) # the return
                    ,ncol=2, byrow=TRUE))

PolList = list(pol1,pol2) #list of lists of numeric matrices
ScndTrail <- sf::st_multipolygon(PolList)
```


## Tree felling
### In 1 function
```{r}
inventory <- treefelling(inventory, scenario = "manual", fuel = "0",
                         directionalfelling = "2", MainTrail = MainTrail, ScndTrail = ScndTrail,
                         advancedloggingparameters = loggingparameters())

Treefall <- inventory %>%
  dplyr::filter(DeathCause == "treefall2nd")

Reserve <- inventory %>%
  dplyr::filter(LoggingStatus == "reserve")

Future <- inventory %>%
  dplyr::filter(LoggingStatus == "future")

ggplot() +
  geom_sf(data = sf::st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
  geom_sf(data = getgeometry (inventory, TreePolygon), fill = "red") + # cuted trees
  geom_sf(data = sf::st_as_sf(Treefall, coords = c("Xutm", "Yutm")), colour = "yellow") +
  geom_sf(data = sf::st_as_sf(Reserve, coords = c("Xutm", "Yutm")), colour = "green") +
  geom_sf(data = sf::st_as_sf(Future, coords = c("Xutm", "Yutm")), colour = "pink")

sf::st_intersection( # trees under the fallen trees
  getgeometry (inventory, TreePolygon),
  sf::st_as_sf(inventory, coords = c("Xutm", "Yutm"))
) %>%
  ggplot() +
  geom_sf()
```

## Quantify the volumes achieved
### Compute the timber harvested volume
```{r}
TimberV <- timberharvestedvolume(inventory, scenario = "manual", fuel = "2",
                                 advancedloggingparameters = loggingparameters())

TimberLoggedVolume <- TimberV$TimberLoggedVolume
NoHollowTimberLoggedVolume <- TimberV$NoHollowTimberLoggedVolume
```

### Compute the exploitable fuel wood volume
```{r}
FuelV <- exploitablefuelwoodvolume(inventory, scenario = "manual", fuel = "2",
                                   TimberLoggedVolume = TimberLoggedVolume,
                                   NoHollowTimberLoggedVolume = NoHollowTimberLoggedVolume,
                                   advancedloggingparameters = loggingparameters())

DamageVolume <- FuelV$DamageVolume # only damage (without purge and hollow trees)
FuelVolume <- FuelV$FuelVolume
```

# Tool functions
```{r include=FALSE}
inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
                        volumeparameters = ForestZoneVolumeParametersTable)
```


## Get geometry
Converts a dataframe with a column of characters, which contains the WKT encoded geometries, into an sf object. The column is converted to sfc.

## Create the canopy
```{r}
canopy <- createcanopy(inventory)

# The small ones first so that they are behind the big ones on the plot
canopy <- dplyr::arrange(canopy, TreeHeight)
ggplot() +
  geom_sf(data = getgeometry(canopy, Crowns),
          aes(alpha = TreeHeight),
          fill = "forestgreen")
```

## 1 tree from the sky
```{r}
dat <- inventory[679,]

Crown <- treefromthesky(dat)

ggplot() +
  geom_sf(data = sf::st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
  geom_sf(data = Crown, fill = "forestgreen") # trees polygons
```

directionalfellingsuccessdef
felling1tree
rotatepolygon





