---
title: "Maria"
subtitle: "Logging simulator"
output: rmarkdown::html_vignette
df_print: kable
vignette: >
  %\VignetteIndexEntry{Maria}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", echo = T, message = T, warning = F, cache = F
)
```

# The different stages of Reduced Impact Logging (RIL) described by the ONF (Office National des Forêts) of French Guiana
1) Definition of the area to be logged
2) The layout of the main skidding trails
3) Tree selection
4) Selection of trees by the logger
5) The layout of secondary skidding trails
6) Felling of the tree
7) Adjustment of secondary skidding trails in the case of Wood Fuel exploitation (WFE)
8) Moving the bole




# Load Maria and datasets
**Install Maria**
```{r, eval=F}
install.packages("Maria")
```
**Load the package**
```{r setup}
library(Maria)
library(knitr)
library(kableExtra)
library(ggplot2)
```
**Load the two datasets stored in the package**
```{r}
# 2016 inventory of Paracou (French Guiana) plot 6
data(Paracou6_2016)
# Table of species exploitability criteria
data(SpeciesCriteria)
# Volume parameters table
data(ForestZoneVolumeParametersTable)
# Crown diameter allometry parameters table
data(ParamCrownDiameterAllometry)
# Digital terrain model (DTM) of the plot 6 of Paracou (1m resolution, LiDAR campaign of 2016)
data(DTMParacou)
# Slopes (in radians) of the plot 6 of Paracou (with a neighbourhood of 8 cells)
data(PlotSlope)
```

# Required format of the inventory
\code{\link{Paracou6_2016}}
```{r}
# inventory class
class(Paracou6_2016)
#The name and class of all the data variables
lapply(Paracou6_2016, class)

Paracou6_2016 %>%
  dplyr::slice(1:10) %>% 
  kable() %>%
  kable_styling(font_size = 10, latex_options = "scale_down")
```
# Required format of the species exploitability criteria
\code{\link{SpeciesCriteria}}
```{r}
# speciescriteria class
class(SpeciesCriteria)
#The name and class of all the data variables
lapply(SpeciesCriteria, class)
kable(SpeciesCriteria)
```
# Required format of the volume parameters
\code{\link{ForestZoneVolumeParametersTable}}
```{r}
# volumeparameters class
class(ForestZoneVolumeParametersTable)
#The name and class of all the data variables
lapply(ForestZoneVolumeParametersTable, class)
kable(ForestZoneVolumeParametersTable)
```
# Required format of the crown diameter allometry parameters
\code{\link{ParamCrownDiameterAllometry}}
```{r}
# crowndiameterparameters class
class(ParamCrownDiameterAllometry)
#The name and class of all the data variables
lapply(ParamCrownDiameterAllometry, class)
kable(dplyr::slice_sample(ParamCrownDiameterAllometry, n=15))
```

# All the functions of the package
loggingsimulation
loggingparameters
scenariosparameters
inventorycheckformat
addtreedim
treeselection
ONFGuyafortaxojoin
harvestable
selected
futurereserve
treefelling
createcanopy
treefromthesky
directionalfellingsuccessdef
felling1tree
rotatepolygon
getgeometry
timberharvestedvolume
exploitablefuelwoodvolume


# Arguments presentation

+ **inventory** : Input inventory (see the inputs formats and metadata in the
\code{\link{vignette}}) (data.frame)

+ **topography** : Digital terrain model (DTM) of the inventoried plot (LiDAR
or SRTM) (RasterLayer)

+ **relativeelevation** : (RasterLayer)

+ **speciescriteria** : Table of species exploitability criteria : species
names, economic interest level, minimum and maximum felling diameter, in
the same format of \code{\link{SpeciesCriteria}} (2 levels of commercial
species) (data.frame)

+ **volumeparameters** : Volume parameters table (in the same format of
\code{\link{ForestZoneVolumeParametersTable}}) to compute the harvestable
volume of each tree, depend to its geographic zone if several locations
(data.frame)

+ **scenario** : Logging scenario: "**RIL1**", "**RIL2broken**", "**RIL2**", "**RIL3**",
"**RIL3fuel**", "**RIL3fuelhollow**" or "**manual**"(character)

+ **objective** : Objective volume per hectare (numeric)

+ **fuel** : Fuel wood exploitation: **no exploitation** = "**0**", **damages and purge**
exploitation in fuel = "**1**", exploitation of **hollow trees, damages and purge** in
fuel = "**2**"

+ **diversification** : Taking of other species in addition to the main
commercial species (2 levels of commercial species in the
\code{\link{SpeciesCriteria}} table) (logical)

+ **winching** : No cable or grapple = "**0**", only **cable** = "**1**", **grapple + cable**
= "**2**"

+ **directionalfelling** : Directional felling = "**0**" (absent), "**1**" (only to
avoid damage to future and reserve trees), "**2**" (avoid damage to future and
reserve trees + track orientation)

+ **specieslax** : Allow diversification if stand is too poor, = FALSE by
default (logical)

+ **objectivelax** : Allow exploitation in case of non-achievement of the
objective volume (if stand too poor), = FALSE by default (logical)

+ **crowndiameterparameters** : Crown diameter allometry parameters table (in
the same format of \code{\link{ParamCrownDiameterAllometry}}) to compute
the crown diameter of each tree, depend to its DBH (Diameter at Breast
Height) and its species, genus or family. (data.frame)

+ **advancedloggingparameters** : Other parameters of the logging simulator
\code{\link{loggingparameters}} (list)

+ **iter** : Number of iterations (numeric). Default = 1.
+ **cores** : Number of cores for parallelization (numeric). Default = 1.

# The scenarios
\code{\link{ScenariosTable}}
```{r}
data(ScenariosTable)
kable(ScenariosTable)
```


# Advanced logging parameters
\code{\link{loggingparameters}}

**Default values**

*Numeric values*

+ **Minimum DBH value** = 10 cm 
+ **Maximum area slope** = 27 % 
+ **Maximum main & 2nd trail centerline slope** = 22 % 
+ **Maximum main & 2nd trail cross slope** = 4 % 
+ **Grapple maximum slope** = 20 % 
+ **Maximum tree slope** = 22 % 
+ **Plateau maximum slope** = 5 % 
+ **Distance to compute slope** = 6 m (3m for each side) 
+ **Water sources buffer zone** = 30 m
+ **Minimum main trail width** = 5 m 
+ **Maximum main trail width** = 6 m 
+ **2nd trail width** = 4 m 
+ **DBH of trees to be avoided at trail construction** = 50 cm 
+ **Objective bonus** = 30 % (20;30%) 
+ **Cable length** = 40 m 
+ **Grapple length** = 6 m 
+ **Minimum distance to consider a tree "isolated"** from other trees of its species = 100 m 
+ **Future trees minimum diameter** = 35 cm 
+ **Proportion of successful directional felling events** = 0.6 %
+ **Minimum orientation of the tree fall to the trail** = 30 degree 
+ **Maximum orientation of the tree fall to the trail** = 45 degree 
+ **Part taken from hollow trees for fuel exploitation** = 1/3 
+ **Purge (unused part of the log)** = 0.14 m^3 of fuel wood/m^3 of logged trees
+ **Maximum trail density** = 200 m/ha (has no impact on the simulation.
A message will only be sent to inform you of its validation or not)
+ **Maximum landing area** = 1500 square meters (has no impact on the simulation.
A message will only be sent to inform you of its validation or not)

*Models*   

+ **Tree harvestable volume** allometry (French Guiana ONF formula):
aCoef + bCoef * (DBH/100)^2,
aCoef and bCoef depend on the forest location, stored in \code{\link{ForestZoneVolumeParametersTable}}, DBH in cm.

+ **Trunk height** allometry (from the cylinder volume formula):
CylinderVolume = pi(((DBH/100)/2)^2 x H,
DBH in cm, height (H) in m. 

+ **Tree height** allometry parameters estimated from Guyanese data with the BIOMASS package:
log(H) = 0.07359191 + 1.34241216 log(DBH) + (-0.12282344)*log(DBH)^2,
height (H) in m, DBH in cm

+ **Crown diameter allometry** (*ref*): ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺,
with 𝜺~N(0,σ^2) and mean σ^2 = 0.0295966977
with the crown diameter (CD) and the tree height (H) in m, and the DBH (D) in cm.

+ **Rotten model**, estimates the tree probability of being probed hollow:
1 / (1 + exp(-(-5.151 + 0.042 DBH))), with DBH in cm 

+ **Visibly defect model**, estimates the tree probability
to have visible defects: 1 / (1 + exp(-(-3.392 + 0.357 * Log(DBH))))
with DBH in cm


# Harvest in 1 function
```{r}
# Rslt <- loggingsimulation(Paracou6_2016,
#                           topography = DTMParacou, relativeelevation  = DTMParacou,
#                           speciescriteria = SpeciesCriteria,
#                           volumeparameters = ForestZoneVolumeParametersTable,
#                           scenario = "manual", objective = 20,
#                           fuel = "2", diversification = TRUE, winching = "2",
#                           directionalfelling = "2", specieslax = FALSE, objectivelax = TRUE,
#                           crowndiameterparameters = ParamCrownDiameterAllometry,
#                           advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
```
The harvestable volume may change from one simulation to another because the identification of defect trees contains a random component.
```{r}
# RIL1_Rslt <- loggingsimulation(Paracou6_2016,
#                                topography = DTMParacou, relativeelevation  = DTMParacou,
#                                speciescriteria = SpeciesCriteria,
#                                volumeparameters = ForestZoneVolumeParametersTable,
#                                scenario = "RIL1", specieslax = FALSE, objectivelax = TRUE,
#                                crowndiameterparameters = ParamCrownDiameterAllometry,
#                                advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary(RIL1_Rslt)
# # Without diversification the harvestable volume is too poor
```

```{r}
# RIL2broken_Rslt <- loggingsimulation(Paracou6_2016,
#                                      topography = DTMParacou, relativeelevation  = DTMParacou,
#                                      speciescriteria = SpeciesCriteria,
#                                      volumeparameters = ForestZoneVolumeParametersTable,
#                                      scenario = "RIL2broken", specieslax = FALSE, objectivelax = TRUE,
#                                      crowndiameterparameters = ParamCrownDiameterAllometry,
#                                      advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary(RIL2broken_Rslt)
# RIL2broken_inventory <- RIL2broken_Rslt$inventory
# # Without diversification the harvestable volume is too poor
# # Not all harvestable trees are always harvested because they are eventually probed hollow, and there is not always a harvestable tree to replace them.
```

```{r}
# RIL2_Rslt <- loggingsimulation(Paracou6_2016,
#                                topography = DTMParacou, relativeelevation  = DTMParacou,
#                                speciescriteria = SpeciesCriteria,
#                                volumeparameters = ForestZoneVolumeParametersTable,
#                                scenario = "RIL2", specieslax = FALSE, objectivelax = TRUE,
#                                crowndiameterparameters = ParamCrownDiameterAllometry,
#                                advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary(RIL2_Rslt)
# # Without diversification the harvestable volume is too poor
```

```{r}
# RIL3_Rslt <- loggingsimulation(Paracou6_2016,
#                                topography = DTMParacou, relativeelevation  = DTMParacou,
#                                speciescriteria = SpeciesCriteria,
#                                volumeparameters = ForestZoneVolumeParametersTable,
#                                scenario = "RIL3", specieslax = FALSE, objectivelax = TRUE,
#                                crowndiameterparameters = ParamCrownDiameterAllometry,
#                                advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# 
# RIL3_inventory <- RIL3_Rslt$inventory
# loggingsummary(RIL3_Rslt)
# # With diversification the harvestable volume is much higher
# # but 30m3/ha is a too high objective for this plot size
# # Not all harvestable trees are always harvested because they are eventually probed hollow, and there is not always a harvestable tree to replace them.
```

```{r}
# RIL3fuel_Rslt <- loggingsimulation(Paracou6_2016,
#                                    topography = DTMParacou, relativeelevation  = DTMParacou,
#                                    speciescriteria = SpeciesCriteria,
#                                    volumeparameters = ForestZoneVolumeParametersTable,
#                                    scenario = "RIL3fuel", specieslax = FALSE, objectivelax = TRUE,
#                                    crowndiameterparameters = ParamCrownDiameterAllometry,
#                                    advancedloggingparameters = loggingparameters(), iter = 1, cores = 1)
# loggingsummary(RIL3fuel_Rslt)
# # Not all harvestable trees are always harvested because they are eventually probed hollow, and there is not always a harvestable tree to replace them.
```

```{r}
# RIL3fuelhollow_Rslt <- loggingsimulation(Paracou6_2016,
#                                          topography = DTMParacou, relativeelevation  = DTMParacou,
#                                          speciescriteria = SpeciesCriteria,
#                                          volumeparameters = ForestZoneVolumeParametersTable,
#                                          scenario = "RIL3fuelhollow",
#                                          specieslax = FALSE, objectivelax = TRUE,
#                                          crowndiameterparameters = ParamCrownDiameterAllometry,
#                                          advancedloggingparameters = loggingparameters(),
#                                          iter = 1, cores = 1)
# RIL3fuelhollow_inventory <- RIL3fuelhollow_Rslt$inventory
# # loggingsummary(RIL3fuelhollow_Rslt)
```

## Results summary
```{r}
# loggingsummary(Rslt)
```

# Decomposed harvesting

## Check & format input inventory data for the "Maria" package
```{r}
inventory <- inventorycheckformat(Paracou6_2016)
```

## Compute tree dimensions
**Tree and crown height and diameter, harvestable volume, wood density, and AGB**
```{r}
inventory <- addtreedim(inventory, volumeparameters = ForestZoneVolumeParametersTable)
```

## Harvestable area definition
By default, a prospecting unit is an area connected to a truck trail or a main skid trail, with a slope of less than 27%, avoiding lowlands and the water system (30 m buffer).
RIL1: SRTM is used.
RIL2broken/RIL2/RIL3/RIL3/RIL3fuel/RIL3fuelhollow: LIDAR is used.

## Tree selection
Trees with visible defects are identified ('VisiblyDefectModel' in 
'advancedloggingparameters' argument) and therefore not designated.

(*Objective volume*: If the user has chosen not to harvest hollow probed trees for
energy ('RottenModel' in 'advancedloggingparameters' argument), 20-30% will be
added to the objective volume in order to compensate for these designated hollow
trees. If the user has chosen to harvest the hollow probed trees as fuel wood,
he will harvest strictly his target volume, without *bonus.*)

Trees will be designated as "**harvestable**" if they:
- belonging to species of 1st economic rank or more if diversification
- DBH between the MinFD and the MaxFD.
- not isolated ( >100m ('IsolateTreeMinDistance') from other individuals of the same species)
- on slopes < 22% ('TreeMaxSlope')
- off the main tracks.

If the harvestable volume is higher than the objective volume, the MinFD of the 1st economic rank species is first increased, then that of the other species (if diversification), if this is not enough. The volume to be harvested is adjusted if necessary by taking the trees in decreasing order of volume, until the objective volume is reached.

If the harvestable volume is too low, diversification can be applied if it was not already applied ('specieslax') (trees of all commercial ranks are selected in decreasing order of volume until the objective volume is reached), or harvesting can continue despite an unreached objective volume, or be abandoned ('objectivelax')

**Future** trees will be:
- species of 1st economic rank
- DBH between 35cm ('FutureTreesMinDiameter') and the species MinFD or UpMinFD if it has been raised for its species. 

**Reserve** trees will be:
- future trees
- in the same number as trees to be harvested.

### In 1 function
**Trees to be exploited, future and reserve trees**
```{r}
# treeselectionoutputs <- treeselection(inventory,
#                                       topography = DTMParacou, plotslope = PlotSlope,
#                                       speciescriteria = SpeciesCriteria,
#                                       objective = 20, scenario ="manual", fuel = "2",
#                                       diversification = FALSE, specieslax = FALSE,
#                                       objectivelax = TRUE,
#                                       advancedloggingparameters = loggingparameters())
```

### Decomposed tree selection
#### Joins commercial criteria table
```{r}
inventory <- ONFGuyafortaxojoin(inventory, SpeciesCriteria)
```

#### Harvestable trees identification
```{r}
harvestableOutputs <- harvestable(inventory, topography = DTMParacou,
                                  diversification = TRUE, plotslope = PlotSlope, specieslax = FALSE,
                                  advancedloggingparameters = loggingparameters())
inventory <- harvestableOutputs$inventory
HVinit <- harvestableOutputs$HVinit
```

#### Trees to be exploited selection
```{r}
inventory <- selected(inventory, scenario = "manual", fuel = "2",
                      diversification = TRUE, VO = 125, HVinit = HVinit, specieslax = FALSE,
                      objectivelax = TRUE, topography = DTMParacou,
                      advancedloggingparameters = loggingparameters())$inventory
```

#### Future & reserve trees designation
```{r}
inventory <- futurereserve(inventory, SpeciesCriteria)
```

## Secondary trails layout

Skidding trail (main, secondary): allows wood to be transported from the parcel to truck routes.

The secondary trails are:
- 4 m width ('ScndTrailWidth')
- 22% maximum slope in length ('MaxTrailCenterlineSlope')
- 4% maximum side slope (taken into account in the presence of LIDAR). ('MaxTrailCrossSlope')
They avoid :
- the trees to be logged
- the trees with a DBH of more than 50 cm ('BigTrees')
- the reserve trees.
They join in priority:
1: groups in decreasing order of tree abundance
2: those with the shortest distance to the nearest track
3: avoiding future trees
4: minimising slopes in length and width.

RIL1/RIL2broken: trails go to the base of trees
RIL2: cable only: trails go up to a maximum of 40 m ('CableLength') from trees.
RIL3/RIL3 including fuel: grapple (trails with longitudinal slope <20% 
('GrappleMaxslope')) (trails go up to 6 m ('GrappleLength') from the trees),
and cable (trails go up to 40 m ('CableLength') from the trees) is used only
when the longitudinal slope is greater than 20% or when the tree to be skidded
is isolated from other trees to be exploited, from 6 to 40 m.
If the crown is not accessible, it will not be harvested, only the trunk can be
used in fuel wood.

If the number of trees connected to a secondary trail exceeds 20 (''), the secondary trail will take the characteristics (width) of a main trail.

Damage :
- on the trail
- on the edge of the trail: neglected.

```{r}
MainTrail <- sf::st_linestring(matrix(c(286400, 583130,
                                        286400, 583250,
                                        286655, 583250,
                                        286655, 583130,
                                        286400, 583130) # the return
                                      ,ncol=2, byrow=TRUE))

pol1 <- list(matrix(c(286503, 583134,
                      286503, 583240,
                      286507, 583240,
                      286507, 583134,
                      286503, 583134) # the return
                    ,ncol=2, byrow=TRUE))
pol2 <- list(matrix(c(286650, 583134,
                      286650, 583240,
                      286654, 583240,
                      286654, 583134,
                      286650, 583134) # the return
                    ,ncol=2, byrow=TRUE))

PolList = list(pol1,pol2) #list of lists of numeric matrices
ScndTrail <- sf::st_multipolygon(PolList)
```


## Tree felling

The felling of the tree creates a tree (including crown) on the ground, with dimensions calculated with specific allometries ('advancedloggingparameters').

RIL1: random fall

RIL2broken/RIL2:
- at 40%: random fall
- at 60% ('TreefallSuccessProportion'): priority 1: *base of the tree towards the nearest trail* (main or 2ndary), priority 2: avoid futures and reserves.

RIL3/RIL3 timber + fuel wood:
- at 40%: random fall
- at 60% ('TreefallSuccessProportion'):
  * if RIL3 + fuel & trees < 6 m from the trail and slope <20% (*grapple* use):
   - no particular angle to orientate to the trail,
    only to orient the tree *crown* as close as possible to the trail
   - priority 1: avoid futures and reserves,
   - priority 2: conformation allowing skidding back to the main trail

  * otherwise (RIL3, RIL3 + fuel &
      trees > 6 m from the trail and/or slope >20%)(*cable* use):
   - 30-45◦ orientation ('MinTreefallOrientation'; 'MaxTreefallOrientation')
   - *base* to nearest trail
   - priority 1: avoid futures and reserves
   - priority 2: conformation allowing skidding back to the main trail

Damage:
Secondary windfall: *all trees under the felled tree (timber or energy) will be considered dead*.

### In 1 function
```{r}
inventory <- treefelling(inventory, scenario = "manual", fuel = "0",
                         directionalfelling = "2", MainTrail = MainTrail, ScndTrail = ScndTrail,
                         advancedloggingparameters = loggingparameters())

Treefall <- inventory %>%
  dplyr::filter(DeathCause == "treefall2nd")

Reserve <- inventory %>%
  dplyr::filter(LoggingStatus == "reserve")

Future <- inventory %>%
  dplyr::filter(LoggingStatus == "future")

ggplot() +
  geom_sf(data = sf::st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
  geom_sf(data = getgeometry (inventory, TreePolygon), fill = "red") + # cuted trees
  geom_sf(data = sf::st_as_sf(Treefall, coords = c("Xutm", "Yutm")), colour = "yellow") +
  geom_sf(data = sf::st_as_sf(Reserve, coords = c("Xutm", "Yutm")), colour = "green") +
  geom_sf(data = sf::st_as_sf(Future, coords = c("Xutm", "Yutm")), colour = "pink")

sf::st_intersection( # trees under the fallen trees
  getgeometry (inventory, TreePolygon),
  sf::st_as_sf(inventory, coords = c("Xutm", "Yutm"))
) %>%
  ggplot() +
  geom_sf()
```

## Quantify the volumes achieved

By default, within a hollow tree, 2/3 of the log will be usable as timber,
1/3 as fuel wood ('TreeHollowPartForFuel').
For dead trees from the operation (trails, secondary windfall),
the whole trunk will be exploitable as fuel wood.

### Compute the timber harvested volume
```{r}
TimberV <- timberharvestedvolume(inventory, scenario = "manual", fuel = "2",
                                 advancedloggingparameters = loggingparameters())

TimberLoggedVolume <- TimberV$TimberLoggedVolume
NoHollowTimberLoggedVolume <- TimberV$NoHollowTimberLoggedVolume
```

### Compute the exploitable fuel wood volume
```{r}
FuelV <- exploitablefuelwoodvolume(inventory, scenario = "manual", fuel = "2",
                                   TimberLoggedVolume = TimberLoggedVolume,
                                   NoHollowTimberLoggedVolume = NoHollowTimberLoggedVolume,
                                   advancedloggingparameters = loggingparameters())

DamageVolume <- FuelV$DamageVolume # only damage (without purge and hollow trees)
FuelVolume <- FuelV$FuelVolume
```

# Tool functions

'inventorycheckformat' check if the input inventory data is compatible with the "Maria" package (see 'Required format of the inventory' section of the vignette)

'addtreedim' compute tree dimensions with the 'advancedloggingparameters' argument:
- Tree height (in m) ('TreeHeightAllometry')
- Tree Harvestable Volume (m^3) ('TreeHarvestableVolumeAllometry')
- Trunk height (in m) ('TrunkHeightAllometry')
- Crown height (in m)
- Crown diameter (in m) ('CrownDiameterAllometry')
- Wood density (g/cm^3) (by BIOMASS package)
- Tree above-ground biomass (AGB) (in Mg) (by BIOMASS package)

```{r include=FALSE}
inventory <- addtreedim(inventorycheckformat(Paracou6_2016),
                        volumeparameters = ForestZoneVolumeParametersTable)
```


## Get geometry
Converts a dataframe with a column of characters, which contains the WKT encoded geometries, into an sf object. The column is converted to sfc.

## Create the canopy

'createcanopy' function return a dataframe with a column 'Crowns' containing the ellipses
(*sfc_POLYGON*) as trees crown, with their diameter filled in,
representing trees from the sky.
```{r}
canopy <- createcanopy(inventory)

# The small ones first so that they are behind the big ones on the plot
canopy <- dplyr::arrange(canopy, TreeHeight)
ggplot() +
  geom_sf(data = getgeometry(canopy, Crowns),
          aes(alpha = TreeHeight),
          fill = "forestgreen")
```

## 1 tree from the sky

'createcanopy' function return an ellipse (*sfc_POLYGON*) as a crown, with its diameter filled in, representing the tree from the sky.
```{r}
dat <- inventory[679,]

Crown <- treefromthesky(dat)

ggplot() +
  geom_sf(data = sf::st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
  geom_sf(data = Crown, fill = "forestgreen") # trees polygons
```

directionalfellingsuccessdef
felling1tree


## Rotate a polygon 
Orient the input polygon to a given angle and fixed point.

```{r}

```






