---
title: "CreekDistances"
author: "Gaquiere Thomas"
date: "17/12/2021"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", echo = T, eval = F
)
```

```{r setup, include=FALSE}
library(Rsagacmd)
library(raster)
```

# Creek Distances computation

## Method 1 : Using Saga-GIS graphical user interface

First step : install SAGA-GIS (Conrad, O., Bechtel, B., Bock, M., Dietrich, H., Fischer, E., Gerlitz, L., Wehberg, J., Wichmann, V., and Böhner, J. (2015): System for Automated Geoscientific Analyses (SAGA) v. 2.1.4, Geosci. Model Dev., 8, 1991-2007, <doi:10.5194/gmd-8-1991-2015>.) : <https://saga-gis.sourceforge.io/>

-   Load the Digital Elevation Model (DEM) (1m resolution) in Saga.

    1.  Execute : Tools -\> Tool Libraries -\> Terrain Analysis -\> Preprocessing -\> Fill Sinks XXL (Wang & Liu) with the loaded DEM and with 'Options : Minimum Slope parameter = 0.1'

        This algorithm will produce a 'filled' DEM.

    2.  Execute : Tools -\> Tool Libraries -\> Hydrology -\> Flow Accumulation (Top-Down) with the filled DEM (1.) as 'Elevation' grid input with default parameters and Method : 'Multiple Flow Direction'.

    3.  Execute : Tools -\> Tool Libraries -\> Terrain Analysis -\> Channels -\> Channel Network with the following inputs :

        -   Elevation : The filled DEM computed in 1.

        -   Initiation Grid : The Flow grid obtained in 2.

        -   Initiation Type : 'Greater than'

        -   Initiation Threshold : minimum number of grid cells required to initiate a channel, with a 1m resolution DEM, we selected a value of 2500. This option may influence in a consequent way the obtained Channel Network (check the Spatial Extent of your DEM before setting this value).

    4.  Execute : Tools -\> Tool Libraries -\> Terrain Analysis -\> Channels -\> Overland Flow Distance to Channel Network with the following inputs :

        -   Elevation : The filled DEM computed in 1.

        -   Channel Network : 'Channel Network' grid computed in 3.

Save 'Vertical Overland Flow Distance' and 'Horizontal Overland Flow Distance' grids as GeoTIFF (\*.tif)

Load the both rasters in your R environment,

-   Vertical Overland Flow Distance : **creekverticaldistance in LoggingLab**

-   Horizontal Overland Flow Distance : **creekhorizontaldistance in LoggingLab**

## Method 2 : Using Saga-GIS and Rsagacmd

First step : install SAGA-GIS and the Rsagacmd package.

Load the Digital Elevation Model (DEM) (1m resolution) in R :

```{r}
DEM <- raster('/YOUR_DEM.tif')
```

Initialize link between Saga-GIS and Rsagacmd :

```{r}
Saga <- saga_gis(verbose=TRUE, raster_backend = "raster", vector_backend = "sf")
```

### 1 - Fill Sinks XXL (Wang & Liu)

```{r}
DEMFilledSinks <- Saga$ta_preprocessor$fill_sinks_xxl_wang_liu(elev = DEM, 
                                                               minslope = .01)
```

### 2 - Flow Accumulation (Top-Down)

```{r}
TotalCatchmentArea <- Saga$ta_hydrology$flow_accumulation_top_down(elevation = DEMFilledSinks, 
                                                                   method = 'Multiple Flow Direction')
```

The 'flow' component of the TotalCatchmentArea object will be used as initiation grid for the channel network computation.

### 3 - Channel Network

```{r}
ChannelNetwork <- Saga$ta_channels$channel_network(elevation = DEMFilledSinks,
                                                   init_grid = TotalCatchmentArea$flow,
                                                   init_method = "Greater than",
                                                   init_value = 2500) 
```

### 4 - Overland Flow Distances To Channel Network

```{r}
CreekDistances <- Saga$ta_channels$overland_flow_distance_to_channel_network(elevation = DEMFilledSinks,
                                                                             channels = ChannelNetwork$chnlntwrk)
```

### 5 - Extract Creek Horizontal and Vertical Distances

```{r}
CreekVerticalDistance <- CreekDistances$distvert # creekverticaldistance 

crs(CreekVerticalDistance) <- crs(DEM) # set the crs

CreekHorizontalDistance <- CreekDistances$disthorz # creekhorizontaldistance 

crs(CreekHorizontalDistance) <- crs(DEM) # set the crs
```
